Physical Chemistry Tips

### 2015-11-22 classical/latex/a7.tex
stuff

\section{Problem Two}

@@

\begin{align*}
  x &= \ell\sin\phi\cos\theta\\
  y &= \ell\sin\phi\sin\theta\\
  \dot{x} &= \ell\cos\phi\cos\theta\dot{\phi} - \ell\sin\phi\sin\theta\dot{\theta}\\
  \dot{y} &= \ell\cos\phi\sin\theta\dot{\phi} + \ell\sin\phi\cos\theta\dot{\theta}\\
  T &= \frac{1}{2}m\left(\ell^2\cos^2\phi\dot{\phi}^2 + \ell^2\sin^2\phi\dot{\theta}^2\right)\\
\end{align*}

@@

>>>>

\section{Problem Two: 3D Pendulum Hamiltonian}

@@

\begin{align*}
  x &= \ell\cos\phi\sin\theta\\
  y &= \ell\sin\phi\sin\theta\\
  z &= \ell\cos\theta\\
  \dot{x} &=  -\ell\sin\phi\sin\theta\dot{\phi} + \ell\cos\phi\cos\theta\dot{\theta}\\
  \dot{y} &= \ell\cos\phi\sin\theta\dot{\phi} + \ell\sin\phi\cos\theta\dot{\theta}\\
  \dot{z} &= -\ell\sin\theta\dot{\theta}\\
  \vspace{1cm}\\
  T &= \frac{1}{2}m\left(\dot{x}^2+\dot{y}^2+\dot{z}^2\right)\\
  &= \frac{1}{2}m\ell^2\left(\sin^2\theta\dot{\phi}^2 + \dot{\theta}^2\right)\\
  U &= mgz = mg\ell\cos\theta\\
  \mathcal{L} &= \frac{1}{2}m\ell^2\left(\sin^2\theta\dot{\phi}^2 + \dot{\theta}^2\right) - mg\ell\cos\theta\\
  \vspace{1cm}\\
  P_{\theta} &= \frac{d\mathcal{L}}{d\dot{\theta}} = m\ell^2\dot{\theta}\\
  P_{\phi} &= \frac{d\mathcal{L}}{d\dot{\phi}} = m\ell^2\sin^2(\theta)\dot{\phi}\\
  \vspace{1cm}\\
  \vspace{1cm}\\
  \mathcal{H} &= P_{\theta}\dot{\theta} + P_{\phi}\dot{\phi} - \mathcal{L}\\
  &= \frac{1}{2}m\ell^2\left(\sin^2\theta\dot{\phi}^2 + \dot{\theta}^2\right) + mg\ell\cos\theta\\
  &= \frac{1}{2}m\ell^2\left(\sin^2\theta\dot{\phi}^2 + \frac{P_{\theta}^2}{m^2\ell^4}\right) + mg\ell\cos\theta\\

    V_{eff}(\theta, P_{\phi}) &=
\end{align*}

\begin{figure}[h]
\caption{Plot of effective potential based on $p_{\phi}$ and gravity potential. Angular momentum linearly adds to the sinusoidal gravity potential.}
\centering
\includegraphics[width=0.5\textwidth]{../v-plot_legend.png}
\end{figure}

\section{Problem Three}
\textbf{A bead of mass m is threaded on a frictionless wire that is bent into a helix with cylindrical polar coordinates (ρ, ϕ, z) satisfying z = cϕ and ρ = R with c and R constants. The z axis points vertically up and gravity vertically down. Using ϕ as your generalized coordinate, write down the kinetic and potential energies and the Hamiltonian H as a function of ϕ and its conjugate momentum p. Write down Hamilton’s equations and solve for φ!!and hence !z!. Explain your result in terms of Newtonian mechanics and discuss the special case that R = 0.}

@@

\begin{align*}
  x &= \ell\sin\phi\cos\theta\\
  y &= \ell\sin\phi\sin\theta\\
  \dot{x} &= \ell\cos\phi\cos\theta\dot{\phi} - \ell\sin\phi\sin\theta\dot{\theta}\\
  \dot{y} &= \ell\cos\phi\sin\theta\dot{\phi} + \ell\sin\phi\cos\theta\dot{\theta}\\
  \vspace{1cm}\\
  T &= \frac{1}{2}m\left(\ell^2\cos^2\phi\dot{\phi}^2 + \ell^2\sin^2\phi\dot{\theta}^2\right)\\
  U &= mgz = mg\ell\cos\theta\\
  \mathcal{L} &= \frac{1}{2}m\left(\ell^2\cos^2\phi\dot{\phi}^2 + \ell^2\sin^2\phi\dot{\theta}^2\right) - mg\ell\cos\theta\\
  \vspace{1cm}\\
  \mathcal{H} &= p_{\theta}\dot{\theta} + p_{\phi}\dot{\phi} - \mathcal{L}\\
  &= m\ell\sin\phi\dot{\theta}^2 + m\ell\cos\phi\dot{\phi}^2 - \frac{1}{2}m\left(\ell^2\cos^2\phi\dot{\phi}^2 + \ell^2\sin^2\phi\dot{\theta}^2\right) + mg\ell\cos\theta\\
  &= \frac{1}{2}m\left(\ell^2\cos^2\phi\dot{\phi}^2 + \ell^2\sin^2\phi\dot{\theta}^2\right) + mg\ell\cos\theta\\
  &= \frac{p_{\theta}^2}{2m} + \frac{p_{\phi}^2}{2m} + mg\ell\cos\theta\\
  V(\theta,p_{\phi}) &= \frac{p_{\phi}^2}{2m} + mg\ell\cos\theta = \frac{1}{2}m\ell^2\cos^2\phi\dot{\phi}^2 + mg\ell\cos\theta\\
\end{align*}

### 2015-11-22 comp_model/latex/paper1.tex
stuff

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header

@@

\title{Effect of Parameters in Phase-Field Model for simulating Solid-Liquid Transitions}
\author{Elliott Capek}

@@

The equation for $\epsilon(\theta)$ is given as follows:

\begin{equation}
  \epsilon = 1 + \delta\cos\left(j\left(\theta_0-\theta\right)\right)
\end{equation}

where $\delta$ is the strength of anisotropy, $j$ is the harmonic number and $\theta_0$ is the angular offset. The higher $j$ is, the more angular ``modes'' will exist in the system.\\

Temperature is also important to this model, as it decides the value of m, the rate of interface front movement. Temperature's time-evolution is given by:

\begin{equation}  \label{eq:dTdt}
  \frac{\partial T}{\partial t} = \nabla^2T + k\frac{\partial \phi}{\partial t}
\end{equation}

where k is the latent heat of the phase change. Liquid freezing into a solid is exergonic, so heat is evolved when $\frac{\partial\phi}{\partial t}$ is positive. \\

@@

Potential f only needs to be defined between $\phi=0$ and $\phi=1$, due to the definition of $\phi$. f should have local minima at $\phi=0$ and $\phi=1$ to encourage settling at either phase and discourage transitional values of $\phi$. The potential is also m-dependent. m is the thermodynamic driving force of the phase-change reaction. It decides if it is favorable or unfavorable to be a solid or liquid, and is a function of T. It will be defined later. Potential depends on m in that the higher m is, the more favorable the liquid phase should be. Sanal presents the following as the phase-transition potential:

\begin{equation}
  f(\phi,m) = \frac{1}{4}\phi^4 - (\frac{1}{2} - \frac{1}{3}m)\phi^3 + (\frac{1}{4}-\frac{1}{2}m)\phi^2
\end{equation}

@@

where $\delta$ is a small value which controls strength of anisotropy, $j$ controls how many angular nodes show up, and $\phi_0$ rotates the crystal. The basic function of $\epsilon$ is to control where the phase-transition should appear, or in this case, how expensive certain angles of the phase transition should be. Certain angles are cheap, and so the system will have the barrier take those on, and some will be expensive, so the system will try and minimize the area of the interface at that angle. In particular, values of $j(\phi_0-\phi)$ close to $-1$ will be favored and values close to $1$ will be disfavored.

The free energy functional is a value that is minimized when a system evolves in time. We can use this fact to time-evolve $\phi$.

>>>>

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header
\renewcommand{\baselinestretch}{1.2}

@@

\title{Using the Phase-Field model for Creating Anisotropic Crystals}
\author{Elliott Capek}

@@

@@

Potential f only needs to be defined between $\phi=0$ and $\phi=1$, due to the definition of $\phi$. f should have local minima at $\phi=0$ and $\phi=1$ to encourage settling at either phase and discourage transitional values of $\phi$. The potential is also m-dependent. m is the thermodynamic driving force of the phase-change reaction. It decides if it is favorable or unfavorable to be a solid or liquid, and is a function of T. Potential depends on m in that the higher m is, the more favorable the liquid phase should be. Sanal presents the following as the phase-transition potential:

\begin{equation}
  f(\phi,m) = \frac{1}{4}\phi^4 - \left(\frac{1}{2} - \frac{1}{3}m\right)\phi^3 + \left(\frac{1}{4}-\frac{1}{2}m\right)\phi^2
\end{equation}

This polynomial meets all the above requirements. See Figure (\ref{fig:f}) for a plot of potential.\\

Thermodynamic driving force m is given by the following equation:

\begin{equation}
  m = \frac{\alpha \tan^{-1}\left(\gamma\left(T_{eq}-T\right)\right)}{\pi}
\end{equation}

where $\alpha \leq 1$ and $\gamma$ are positive constants. By this definition, $|m| \leq \frac{1}{2}$.

\begin{figure}[h!]
  \caption{\textbf{A plot of $f(\phi,m)$ for different values of m. Notice that all lines have minima at $\phi=0$ and $\phi=1$. The general trend is higher values of m have higher potentials for the solid phase. At m=0, there is an equal potential for solid and liquid phase, hence this is the equilibrium m (corresponding to an equilibrium temperature).}}
  \centering
  \includegraphics[width=0.5\textwidth]{../f_plot.png}
  \label{fig:f}
\end{figure}

@@

where $\delta$ is a small value which controls strength of anisotropy, $j$ controls how many angular nodes show up, and $\phi_0$ rotates the crystal. The basic function of $\epsilon$ is to control where the phase-transition should appear, or in this case, how expensive certain angles of the phase transition should be. Certain angles are cheap, and so the system will have the barrier take those on, and some will be expensive, so the system will try and minimize the area of the interface at that angle. In particular, values of $j(\phi_0-\phi)$ close to $-1$ will be favored and values close to $1$ will be disfavored.\\

The free energy functional is a value that is minimized when a system evolves in time. We can use this fact to time-evolve $\phi$. Intuitively we know that, if we want to minimize F by changing $\phi$, we should couple $\frac{\partial\phi}{\partial t}$ to the functional derivative $\frac{\delta F}{\delta \phi}$, or how much free energy is changing with respect to a change in $\phi$. Sanal does this as follows:

\begin{equation}
  \tau \frac{\partial \phi}{\partial t} = \frac{\delta F}{\delta \phi}
\end{equation}

where $\tau$ is a small positive parameter which controls the proportionality of the two derivatives. This functional derivative is difficult to evaluate. We can transform this equation into a simpler numerical one like so:

\begin{equation}
  \tau \frac{d\phi_{ij}}{dt} = \frac{dF_{ij}}{d\phi_{ij}}
  \label{eq:phi-evol}
\end{equation}

Becuse we are on a two-dimensional grid, we can compartmentalize $\phi$, so $\phi_{ij}$ is the $(i,j)$ element on our grid. Free energy F is an integral over the entire system, but we can compartmentalize it to the following:

\begin{equation}
  F_{ij}(\phi_{ij}) = f(\phi_{ij},m) + \frac{\epsilon(\phi_{ij})^2}{2}|\nabla\phi_{ij}|^2
\end{equation}

where we have removed the volume integral on the total F. We can see that $F = \sum_i \sum_j F_{ij}$, so minimizing F is equivalent to minimizing $F_{ij}$ for all values of $i,j$. We have transformed the functional F into a simple function $F_{ij}$.\\

NOTE: One problem with Equation (\ref{eq:phi-evol}) to me is that $\tau$ should be negative. It seems that if $\frac{dF_{ij}}{d\phi_{ij}}$ is positive, then $\frac{d\phi_{ij}}{dt}$ should be negative, so as to make sure $F_{ij}$ is always decreasing as time increases. However, this equation seems to predict the opposite.\\

We then take the $\phi$ derivative of the RHS of Equation (\ref{eq:phi-evol}) and get the following:

\begin{equation}
  \tau \frac{d\phi_{ij}}{dt} = \frac{\partial}{\partial x}\left(\epsilon_{ij}\frac{\partial \epsilon_{ij}}{\partial \phi_{ij}}\frac{\partial \phi_{ij}}{\partial y}\right) + \frac{\partial}{\partial y}\left(\epsilon_{ij}\frac{\partial \epsilon_{ij}}{\partial \phi}\frac{\partial \phi_{ij}}{\partial x}\right) + \epsilon_{ij}^2\nabla^2\phi_{ij} + \phi_{ij}\left(1-\phi_{ij}\right)\left(\phi_{ij}-0.5+m\right)
\end{equation}

The fourth term is a rearrangement of $-\frac{\partial f}{\partial\phi}$. The first three terms are part of the product rule derivation of $\frac{\epsilon^2}{2}|\nabla\phi|^2$. This equation is in a form that we can evaluate numerically.

\section{Derivation of T-evolution}

Temperature evolution is done with the following equation:

\begin{equation}
  \frac{\partial T}{\partial t} = \nabla^2 T + K\frac{\partial\phi}{\partial t}
\end{equation}

The first term is the normal heat equation, where heat is passed from high-temperature elements to low-temperature elements. The second term is the heat evolved from the transition from liquid to solid. K is the latent heat, which describes how much heat is released at this transition.

\section{Simulation}
Now that we have our time-evolution equations, it is a simple matter to solve for $\phi$ over time. We do this by using the forwards-Euler method on equations (11) and (12), which requires us to compute spacial derivatives of $\frac{\partial}{\partial x}\left(\epsilon_{ij}\frac{\partial \epsilon_{ij}}{\partial \phi_{ij}}\frac{\partial \phi_{ij}}{\partial y}\right)$ and $\frac{\partial}{\partial y}\left(\epsilon_{ij}\frac{\partial \epsilon_{ij}}{\partial \phi}\frac{\partial \phi_{ij}}{\partial x}\right)$, as well as the Laplacian of both $\epsilon$ and $\phi$. We compute the spacial derivatives of the functions by taking the difference between the values at neighboring points (using periodic boundary conditions). We use a nine-point Laplacian using the considered point and the eight points adjacent to it, weighting the adjacent points $+\frac{2}{3}$ and the considered point $-4$.

\section{Reference}
        \hspace{2cm}[1] Sanal, Rahul. Numerical Simulation of Dendritic crystal growth using phase field method and investigating the effects of different physical parameter on the growth of the dendrite. Arxiv.<arxiv.org/ftp/arxiv/papers/1412/1412.3197.pdf>\\

### 2015-11-22 physical_chemistry/latex/pchem_tips.tex
stuff

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{ifsym} % Required for symbols in the colored box

@@

\title{Classical Mechanics Assignment 6}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

\begin{document}

@@

\section{Problem One: Ball on an Inclined Plane}
\textbf{Write the Lagrangian for a cylinder (mass m, radius R, and moment of inertia I) that rolls without slipping straight down an inclined plane at an angle $\alpha$ from the horizontal. Use as your generalized coordinates the cylinder’s distance x measured down the plane from its starting point. Solve the Lagrange equation for the cylinder’s acceleration $\ddot{x}$. Remember that $T = \frac{1}{2} mv^2 + \frac{1}{2} I\omega^2$ where $v$ is the velocity of the center of mass and $\omega$ is the cylinder’s angular velocity.}

\begin{align*}
  x' &= x\cos(\alpha)\\
  y' &= -x\sin(\alpha)\\
  \omega &= \frac{v}{2\pi R}\\
  \vspace{1cm}\\
  U &= mgy' = -mgx\sin(\alpha)\\
  T &= \frac{1}{2}mv^2 + \frac{1}{2}I\omega^2\\
  &= \frac{1}{2}m\left(\dot{x}'^2 + \dot{y}'^2\right) + \frac{1}{2}I\left(\frac{\dot{x}'^2 + \dot{y}'^2}{2\pi R}\right)\\
  &= \frac{1}{2}m\left(\dot{x}^2\sin^2(\alpha) + \dot{x}^2\cos^2(\alpha)\right) + \frac{1}{2}I\left(\frac{\dot{x}^2\sin^2(\alpha) + \dot{x}^2\cos^2(\alpha)}{4\pi^2R^2}\right)\\
  &= m\left(\dot{x}^2\right) + I\left(\frac{\dot{x}^2}{4\pi^2R^2}\right)\\
  &= \dot{x}^2\left(\frac{I + 4\pi^2R^2m}{4\pi^2R^2}\right)\\
  L &= \dot{x}^2\left(\frac{I + 4\pi^2R^2m}{4\pi^2R^2}\right) + mgx\sin(\alpha)\\
  \vspace{1cm}\\
  &\frac{dL}{dx} - \frac{d}{dt}\frac{dL}{d\dot{x}} = 0\\
  &mg\sin(\alpha) - \ddot{x}\left(\frac{I + 4\pi^2R^2m}{\pi^2R^2}\right) = 0\\
  \ddot{x} &= \frac{\pi^2R^2mg\sin(\alpha)}{I + 4\pi^2R^2m}\\
  x &= \frac{\pi^2R^2mg\sin(\alpha)}{2I + 8\pi^2R^2m}t^2
\end{align*}

It took me a while to figure out why I needed to set up kinetic energy in cartesian coordinates. I thought I could just take my axes to be in the x direction (down the slope), but that isn't how we've done other problems. Although I did use the cartesian coordinates method, I found that using other cartesian coordinates (ones more natural to the problem, where x is in the direction of the wedge) would have yielded the same answer. I will try to apply these smarter cartesian coordinates to further problems.\\

\section{Problem Two: Bead on a Spiral}
\textbf{A smooth wire is bent into the shape of a helix, with cylindrical coordinates $\rho=R$ and $z=\lambda\phi$, where $R$ and $\lambda$ are constants and the z axis is vertically up (and gravity is vertically down). Using z as your generalized coordinate, write down the Lagrangian for a bead of mass m threaded on the wire. Find the Lagrange equation and the bead’s vertical acceleration $\ddot{z}$. In the limit that $R → 0$, what is $\ddot{z}$? Does this make sense?}

\begin{align*}
  v &= \sqrt{\dot{\rho}^2 + \rho^2\dot{\phi}^2 + \dot{z}^2}\\
  &= \sqrt{\rho^2\frac{\dot{z}^2}{\lambda^2} + \dot{z}^2}\\
  \vspace{1cm}\\
  T &= \frac{1}{2}mv^2\\
  &= \frac{1}{2}m\left(\rho^2\frac{\dot{z}^2}{\lambda^2} + \dot{z}^2\right)\\
  U &= mgz\\
  L &= \frac{1}{2}m\left(\rho^2\frac{\dot{z}^2}{\lambda^2} + \dot{z}^2\right) - mgz\\
  \vspace{1cm}\\
  &\frac{dL}{dz} - \frac{d}{dt}\frac{dL}{d\dot{z}} = 0\\
  -mg - \ddot{z}m\left(\frac{\rho^2}{\lambda^2}+1\right) &= 0\\
  \ddot{z} &= \frac{-g}{\frac{R^2}{\lambda^2}+1}\\
\end{align*}

Fun problem. It was simple and easy to set up. It was interesting to think about how the problem would be different if the helix was moving. Also, when R goes to zero, the rhs of the equation just turns to -g, which is exactly what you would expect: a frictionless bead falling down a straight loop. It was cool that this works out.\\

\section{Problem Three: }
\textbf{Write the Lagrangian for a cylinder (mass m, radius r, and moment of inertia $I=\frac{mr^2}{2}$) that rolls without slipping in the bottom of a circular shaped hole of equation $z = −\sqrt{R^2 − x^2}$ , where z is the vertical axis (see figure below). Find the angular frequency of small oscillations about the bottom of the hole.}

\begin{align*}
  x &= (R-r)\sin(\theta)\\
  z &= -(R-r)\cos(\theta)\\
  v^2 &= (R-r)^2\dot{\theta}^2\\
  \omega^2 &= \frac{v^2}{r^2} = \frac{(R-r)^2\dot{\theta}^2}{r^2}\\
  \vspace{1cm}\\
  T &= \frac{1}{2}mv^2 + \frac{1}{2}I\omega^2\\
  &= \frac{1}{2}m(R-r)^2\dot{\theta}^2 + \frac{1}{2}I\frac{(R-r)^2\dot{\theta}^2}{r^2}\\
  &= \frac{1}{2}\left(m + \frac{I}{r^2}\right)(R-r)^2\dot{\theta}^2\\
  U &= -mg(R-r)\cos(\theta)\\
  L &= \frac{1}{2}\left(m + \frac{I}{r^2}\right)(R-r)^2\dot{\theta}^2 + mg(R-r)\cos(\theta)\\
  \vspace{1cm}\\
  \frac{dL}{d\theta} - \frac{d}{dt}\frac{dL}{d\dot{\theta}} &= 0\\
  -mg(R-r)\sin(\theta) - \left(m + \frac{I}{r^2}\right)(R-r)^2\ddot{\theta} &= 0\\
  \left(m + \frac{I}{r^2}\right)(R-r)\ddot{\theta} &= -mg\sin(\theta)\\
  \ddot{\theta} &= \frac{-mg\sin(\theta)}{\left(m + \frac{I}{r^2}\right)(R-r)}\\
  \ddot{\theta} &= \frac{-2g\sin(\theta)}{3(R-r)}\\
\end{align*}

We then take the small angle approximation:

\begin{align*}
  \ddot{\theta} &= \frac{-2g\theta}{3(R-r)}\\
\end{align*}

Suppose our solution for $\theta$ takes the form $\theta = e^{wt}$. Then we can see that $\omega = \sqrt{\frac{2g}{3(R-r)}}$.\\

Cool problem! It felt nice to get a final result that looks like that of a pendulum, even though we used a completely different method. The small angle approximation helped a lot for this problem, I was struggling at applying it for a while. Remembering how to find the angular frequency was good for me, the method of guessing the solution takes the form of a pendulum solution and comparing the solutions together to create new information is cool.\\

\section{Problem Four: }
\textbf{The figure below shows a simple pendulum (mass m, length l) whose point of support P is attached to the edge of a wheel (center O, radius R) that is forced to rotate at a fixed angular velocity $\omega$. At t=0, the point P is level with O on the right. Write the Lagrangian and find the equation of motion for the angle $\phi$. [Hint: Be careful writing down the kinetic energy T. A safe way to get the velocity right is to write down the position of the bob at time t, and then differentiate.] Check that your answer makes sense in the special case that $\omega=0$.}
\begin{align*}
  x &= R\cos(\omega t) + l\sin(\phi)\\
  y &= R\sin(\omega t) - l\cos(\phi)\\
  \dot{x} &= -\omega R\sin(\omega t) + l\cos(\phi)\dot{\phi}\\
  \dot{y} &= \omega R\cos(\omega t) + l\sin(\phi)\dot{\phi}\\
  \vspace{1cm}\\
  T &= \frac{1}{2}mv^2\\
  &= \frac{1}{2}m\left(\omega^2R^2\sin^2(\omega t) + l^2\cos^2(\phi)\dot{\phi}^2 - 2\omega Rl\sin(\omega t)\cos(\phi)\dot{\phi} + \omega^2 R^2\cos^2(\omega t) + l^2\sin^2(\phi)\dot{\phi}^2 + 2\omega Rl\cos(\omega t)\sin(\phi)\dot{\phi}\right)\\
  &= \frac{1}{2}m\left(\omega^2R^2 + l^2\dot{\phi}^2 + 2\dot{\phi}\omega Rl\left(\cos(\omega t)\sin(\phi) - \sin(\omega t)\cos(\phi)\right)\right)\\
  &= \frac{1}{2}m\left(\omega^2R^2 + l^2\dot{\phi}^2 + 2\dot{\phi}\omega Rl\sin(\phi - \omega t)\right)\\
  U &= mgy = mg\left(R\sin(\omega t) - l\cos(\phi)\right)\\
  L &= \frac{1}{2}m\left(\omega^2R^2 + l^2\dot{\phi}^2 + 2\dot{\phi}\omega Rl\sin(\phi - \omega t)\right) - mg\left(R\sin(\omega t) - l\cos(\phi)\right)\\
  &= \frac{m\omega^2R^2}{2} + \frac{ml^2\dot{\phi}^2}{2} + m\dot{\phi}\omega Rl\sin(\phi - \omega t) - mg\left(R\sin(\omega t) - l\cos(\phi)\right)\\
  \vspace{1cm}\\
  &\frac{dL}{d\phi} - \frac{d}{dt}\frac{dL}{d\dot{\phi}} = 0\\
  &\frac{dL}{d\phi} = m\dot{\phi}\omega Rl\cos(\phi - \omega t) - mgl\sin(\phi)\\
  &\frac{dL}{d\dot{\phi}} = ml^2\dot{\phi} + m\omega Rl\sin(\phi - \omega t)\\
  &\frac{d}{dt}\frac{dL}{d\dot{\phi}} = ml^2\ddot{\phi} - m\omega Rl\cos(\phi - \omega t)\left(\dot{\phi} - \omega\right)\\
  &m\dot{\phi}\omega Rl\cos(\phi - \omega t) - mgl\sin(\phi) - ml^2\ddot{\phi} + m\omega Rl\cos(\phi - \omega t)\left(\dot{\phi} - \omega\right) = 0\\
  &\omega^2R\cos(\phi - \omega t) + g\sin(\phi) = l\ddot{\phi}\\
\end{align*}

This solution makes sense because, for the case where $\omega = 0$, the equation would be just $g\sin(\phi) = l\ddot{\phi}$, which is the equation for a pendulum. This was a cool problem, I feel like I'm getting experienced at using Lagrangians. Applying the equation of tangential velocity was also something I had to remember how to do. I think it's interesting that coming at the problem from different angles (cartesian coordinates in one direction or another) will yield the same answer.\\

>>>>

\usepackage{amsmath}
\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

@@

\title{Physical Chemistry Tips}
\begin{document}

@@

\section{Random relationships}

\subsection{Weird unknown axioms}

\begin{align*}
  \frac{dH}{dP}_t &= -T\frac{dV}{dT}_P + V\\
\end{align*}

\begin{align*}
  \frac{dQ}{T} &= dS\\
  TdS &= (dH)_p = C_pdT\\
  \frac{dS}{dT} &=\frac{C_p}{T}\\
\end{align*}
